A memory frontier for complex synapses: Supplementary material

### 2013-10-17 NIPS/SynapseNIPSsupp.tex
typos

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{A memory frontier for complex synapses: Supplementary material}
%
% Author List:
%
\author{Subhaneil Lahiri and Surya Ganguli\\
Applied Physics Department, Stanford University, Stanford CA\\
\emaillink{sulahiri@stanford.edu}, \emaillink{sulahiri@stanford.edu}
%
}

@@

Let us denote the set of states by $\CS$.
Consider a subset $\CA\subset\CS$.
We can define a projection operator onto this subset:
%
\begin{equation}\label{eq:proj}
  \prn{\I^\CA}_{ij} =
    \begin{cases}
      1 &\text{if $i=j\in\CA$,}\\
      0 &\text{otherwise.}
    \end{cases}
\end{equation}
%
We will use superscripts/subscripts to denote projection onto/summation over a subset:
%
\begin{equation}\label{eq:projsum}
  \begin{aligned}
    \pib^\CA &=\pib\I^\CA, &
    \M^{\cdot\CA}&=\M\I^\CA, &
    \M^{\CA\cdot}&=\I^\CA\M, &
    \mathbf{x}^\CA &= \I^\CA\mathbf{x},
    \\
    \pib_\CA &=\pib\onev^\CA, &
    \M_{\cdot\CA}&=\M\onev^\CA, &
    \M_{\CA\cdot}&=\prn{\onev^\CA}\trans\M, &
    \mathbf{x}_\CA &= \prn{\onev^\CA}\trans\mathbf{x},
  \end{aligned}
\end{equation}
%
where $\pib$ is a row vector, $\CM$ is a matrix and $\mathbf{x}$ is a column vector.

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{A memory frontier for complex synapses: Supplementary material}
%
% Author List:
%
\author{Subhaneil Lahiri and Surya Ganguli\\
Department of Applied Physics, Stanford University, Stanford CA\\
\emaillink{sulahiri@stanford.edu}, \emaillink{sulahiri@stanford.edu}
%
}

@@

Let us denote the set of states by $\CS$.
Consider a subset $\CA\subset\CS$.
We can define a projection operator onto this subset:
%
\begin{equation}\label{eq:proj}
  \prn{\I^\CA}_{ij} =
    \begin{cases}
      1 &\text{if $i=j\in\CA$,}\\
      0 &\text{otherwise.}
    \end{cases}
\end{equation}
%
We will use superscripts/subscripts to denote projection onto/summation over a subset:
%
\begin{equation}\label{eq:projsum}
  \begin{aligned}
    \pib^\CA &=\pib\I^\CA, &
    \M^{\cdot\CA}&=\M\I^\CA, &
    \M^{\CA\cdot}&=\I^\CA\M, &
    \mathbf{x}^\CA &= \I^\CA\mathbf{x},
    \\
    \pib_\CA &=\pib\onev^\CA, &
    \M_{\cdot\CA}&=\M\onev^\CA, &
    \M_{\CA\cdot}&=\prn{\onev^\CA}\trans\M, &
    \mathbf{x}_\CA &= \prn{\onev^\CA}\trans\mathbf{x},
  \end{aligned}
\end{equation}
%
where $\pib$ is a row vector, $\M$ is a matrix and $\mathbf{x}$ is a column vector.
